Retrofitting Effect Handlers onto OCaml

### 2021-03-24 retro-concurrency.tex
avoid breaking on bullet numbers

\begin{abstract}
Effect handlers have been gathering momentum as a mechanism for modular
	programming with user-defined effects. Effect handlers allow for non-local
	control flow mechanisms such as generators, async/await, lightweight threads
	and coroutines to be composably expressed.  We present a design and evaluate
	a full-fledged efficient implementation of effect handlers for OCaml, an
	industrial-strength multi-paradigm programming language. Our implementation
	strives to maintain the backwards compatibility and performance profile of
	existing OCaml code. Retrofitting effect handlers onto OCaml is challenging
	since OCaml does not currently have any non-local control flow mechanisms
	other than exceptions. Our implementation of effect handlers for OCaml: {\em
	(i)} imposes a mean 1\% overhead on a comprehensive macro benchmark suite
	that does not use effect handlers; {\em (ii)} remains compatible with program
	analysis tools that inspect the stack; and {\em (iii)} is efficient for new
	code that makes use of effect handlers.
\end{abstract}

>>>>

\begin{abstract}
Effect handlers have been gathering momentum as a mechanism for modular
	programming with user-defined effects. Effect handlers allow for non-local
	control flow mechanisms such as generators, async/await, lightweight threads
	and coroutines to be composably expressed.  We present a design and evaluate
	a full-fledged efficient implementation of effect handlers for OCaml, an
	industrial-strength multi-paradigm programming language. Our implementation
	strives to maintain the backwards compatibility and performance profile of
	existing OCaml code. Retrofitting effect handlers onto OCaml is challenging
	since OCaml does not currently have any non-local control flow mechanisms
	other than exceptions. Our implementation of effect handlers for OCaml: {\em
	(i)}~imposes a mean 1\% overhead on a comprehensive macro benchmark suite
	that does not use effect handlers; {\em (ii)}~remains compatible with program
	analysis tools that inspect the stack; and {\em (iii)}~is efficient for new
	code that makes use of effect handlers.
\end{abstract}
